---
title: "2018 BAM Workplan"
author: "Table: BAM's Project Structure"
---

**Last run: `r format(Sys.Date(), "%B %e, %Y")`**

* BAM pursues **projects** in four parallel but inter-connected **domains**. 
* Within domains, projects are organized by overarching **themes**
* Projects working towards the same end goal are clustered into a single **cluster**. 
* A **Project** it typically discrete, and results in an end result such as a paper or report. 


# Plot in summarized, hierarchical format. 

## import projects in flat database format

``` {r}
projs <- read.csv("dataTables/qry_bamPROJECTSflat.csv", header=T)
```

### Add back in lookup tables and corresponding colours
``` {r}
## Project Status
status <- read.csv("dataTables/lookup_projectSTATUS.CSV", header=T)
colnames(projs)[which(colnames(projs)=="projectSTATUS")] <- "ID"
projs <- merge(projs, status, by="ID", all.x=T)
projs <- projs[-1]

## Project proximity
proximity <- read.csv("dataTables/lookup_projectPROXIMITY.csv", header=T)
colnames(projs)[which(colnames(projs)=="Proximity")] <- "ID"
projs <- merge(projs, proximity, by="ID", all.x=T)
projs <- projs[-1]

## Leads
leads <- read.csv("dataTables/bamPEOPLE.csv", header=T)
colnames(projs)[which(colnames(projs)=="LEAD")] <- "fullNAME"
projs <- merge(projs, leads[c("fullNAME", "personColour")], by="fullNAME", all.x=T)
```

``` {r}
projs1 <- projs[c("domainNAME", "themeNAME", "clusterNAME", "PROJECTname", "PROJECTpurpose", "nature", "projectSTATUS", "Proximity")]
projs1$size <- 1
```

## Tree map

``` {r, fig.height=11, fig.width=8.5, eval=F}
require(treemap)
treemap(projs1, index=colnames(projs1[1:5]), vSize="size")

trash <- lapply(1:4, function(i) {
  treemap(projs1[projs1$domainNAME %in% unique(projs1$domainNAME)[i],], index=colnames(projs1[2:5]), vSize="size")
})
```

Pretty, but not information rich enough for my purposes. 

# Dynamic split screen based on data.frame contents

``` {r}
F.hierarcplot <- function(dat,
         col1L = 0, 
         col2L = 0.1, 
         col3L = 0.2, 
         col4L = 0.35,
         col5L = 0.6,
         col5R = 1,
         wrapsize1=9,
         wrapsize2=12,
         wrapsize3=15,
         wrapsize4=35,
         wrapsize5=45,
         fontsize1=1, 
         fontsize2=1,
         fontsize3=1,
         fontsize4=0.75,
         fontsize5=0.5,
         domcol="white", 
         thmcol="white", 
         cluscol="white", 
         projcol="white", 
         detcol="white",
         clrcol="StatusColour")

 {
# dat is a data frame containing the hierarchically-organized information. 
# column coordinates are set  based on expected content. Default values are what last worked for mine. 
# note this function is written for 5 columns and isn't flexible to other options.

#PROJECT COLUMN
# determine number of rows and sizes for project column
projcoor <- data.frame(L=rep(col4L, times=nrow(dat)),
                       R=rep(col5L, times=nrow(dat)),
                       B=rep(NA, times=nrow(dat)),
                       T=rep(NA, times=nrow(dat)))

for (i in 1:nrow(projcoor)) {
  projcoor[i,3] <- 1 - (i / nrow(projcoor)) # bottom coordinate
  projcoor[i,4] <- 1 - ((i-1)/nrow(projcoor)) # top coordinate
}

# determine number of rows and sizes for project detail column
detcoor <- data.frame(L=rep(col5L, times=nrow(dat)),
                       R=rep(col5R, times=nrow(dat)),
                       B=rep(NA, times=nrow(dat)),
                       T=rep(NA, times=nrow(dat)))

for (i in 1:nrow(detcoor)) {
  detcoor[i,3] <- 1 - (i / nrow(detcoor)) # bottom coordinate
  detcoor[i,4] <- 1 - ((i-1)/nrow(detcoor)) # top coordinate
}


# determine number of rows and sizes for  cluster column
uniqueclus <- length(unique(dat$clusterNAME))
cluscoor <- data.frame(L=rep(col3L, times=uniqueclus),
                       R=rep(col4L, times=uniqueclus),
                       B=rep(NA, times=uniqueclus),
                       T=rep(NA, times=uniqueclus))

for (i in 1:nrow(cluscoor)) {
  if (i == 1) {
    nproj.in.prevclus <- 0
    ithclus <- unique(dat$clus)[i]
    nproj.in.ithclus <-  length(dat$PROJECTname[dat$clusterNAME %in% ithclus])
  } else {
    prevclus <- unique(dat$clus)[1:(i-1)] # clusters previously populated 
    nproj.in.prevclus <-  length(dat$PROJECTname[dat$clusterNAME %in% prevclus]) # number of projects within previously populated clusters
    
    ithclus <- unique(dat$clus)[i] # cluster to populate on ith iteration
    nproj.in.ithclus <- length(dat$PROJECTname[dat$clusterNAME %in% ithclus]) # number of projects within this cluster
  }
    
  cluscoor[i,3] <- 1 - ((nproj.in.ithclus + nproj.in.prevclus) / nrow(dat)) # bottom coordinate
  
  cluscoor[i,4] <- 1 - (nproj.in.prevclus/nrow(dat))  # top coordinate
}

# determine number of rows and sizes for  theme column
uniquetheme <- length(unique(dat$themeNAME))
themecoor <- data.frame(L=rep(col2L, times=uniquetheme),
                       R=rep(col3L, times=uniquetheme),
                       B=rep(NA, times=uniquetheme),
                       T=rep(NA, times=uniquetheme))

for (i in 1:nrow(themecoor)) {
  if (i == 1) {
    nproj.in.prevtheme <- 0
    iththeme <- unique(dat$themeNAME)[i]
    nproj.in.iththeme <-  length(dat$PROJECTname[dat$themeNAME %in% iththeme])
  } else {
    prevtheme <- unique(dat$themeNAME)[1:(i-1)] # themes previously populated 
    nproj.in.prevtheme <-  length(dat$PROJECTname[dat$themeNAME %in% prevtheme]) # number of projects within previously populated themes
    
    iththeme <- unique(dat$themeNAME)[i] # cluster to populate on ith iteration
    nproj.in.iththeme <- length(dat$PROJECTname[dat$themeNAME %in% iththeme]) # number of projects within this theme
  }
    
  themecoor[i,3] <- 1 - ((nproj.in.iththeme + nproj.in.prevtheme) / nrow(dat)) # bottom coordinate
  
  themecoor[i,4] <- 1 - (nproj.in.prevtheme/nrow(dat))  # top coordinate
}

# determine number of rows and sizes for  domain column
uniquedomain <- length(unique(dat$domainNAME))
domaincoor <- data.frame(L=rep(col1L, times=uniquedomain),
                       R=rep(col2L, times=uniquedomain),
                       B=rep(NA, times=uniquedomain),
                       T=rep(NA, times=uniquedomain))

for (i in 1:nrow(domaincoor)) {
  if (i == 1) {
    nproj.in.prevdomain <- 0
    ithdomain <- unique(dat$domainNAME)[i]
    nproj.in.ithdomain <-  length(dat$PROJECTname[dat$domainNAME %in% ithdomain])
  } else {
    prevdomain <- unique(dat$domainNAME)[1:(i-1)] # themes previously populated 
    nproj.in.prevdomain <-  length(dat$PROJECTname[dat$domainNAME %in% prevdomain]) # number of projects within previously populated domains
    
    ithdomain <- unique(dat$domainNAME)[i] # cluster to populate on ith iteration
    nproj.in.ithdomain <- length(dat$PROJECTname[dat$domainNAME %in% ithdomain]) # number of projects within this domain
  }
    
  domaincoor[i,3] <- 1 - ((nproj.in.ithdomain + nproj.in.prevdomain) / nrow(dat)) # bottom coordinate
  
  domaincoor[i,4] <- 1 - (nproj.in.prevdomain/nrow(dat))  # top coordinate
}

# COMBINE ALL COORDINATES INTO ONE BIG MATRIX.
allcoor <- rbind(domaincoor, themecoor, cluscoor, projcoor, detcoor)

texttoprint <- c(as.character(dat$domainNAME[!duplicated(dat$domainNAME)]),
as.character(dat$themeNAME[!duplicated(dat$themeNAME)]),
as.character(dat$clusterNAME[!duplicated(dat$clusterNAME)]),
as.character(dat$PROJECTname),
as.character(dat$PROJECTpurpose))

wraplength <- c(rep(wrapsize1, times=length(unique(dat$domainNAME))), # domain
                rep(wrapsize2, times=length(unique(dat$themeNAME))), #theme
                rep(wrapsize3, times=length(unique(dat$clusterNAME))), #cluster
                rep(wrapsize4, times=length(dat$PROJECTname)), #project
                rep(wrapsize5, times=length(dat$PROJECTpurpose))) #purpose

fontsize <- c(rep(fontsize1, times=length(unique(dat$domainNAME))), # domain
                rep(fontsize2, times=length(unique(dat$themeNAME))), #theme
                rep(fontsize3, times=length(unique(dat$clusterNAME))), #cluster
                rep(fontsize4, times=length(dat$PROJECTname)), #project
                rep(fontsize5, times=length(dat$PROJECTpurpose))) #purpose

bgcolour <- c(rep(domcol, times=length(unique(dat$domainNAME))), # domain
                rep(thmcol, times=length(unique(dat$themeNAME))), #theme
                rep(cluscol, times=length(unique(dat$clusterNAME))), #cluster
                as.character(dat[[clrcol]]), #project
                as.character(dat[[clrcol]])) #purpose

split.screen(as.matrix(allcoor))

for(i in 1:nrow(allcoor)) {
 par(bg=bgcolour[i])
 screen(i)
 par(mar = c(0, 0, 0, 0))
 text(.5,.5,paste(strwrap(texttoprint[i],wraplength[i]), collapse="\n"), cex=fontsize[i])
 box()
 par(bg="white")
 }

 close.screen(all.screens = TRUE)
         }

```

## All projects in all themes at once 

Note, if you run this chunk the whole script won't read to markdown output. Fails at pandoc

``` {r, eval=T, fig.height=11, fig.width=8.5, dpi=100, dev='tiff', fig.path="figures/", eval=F}

trash <- lapply(1:length(unique(projs$domainNAME)), function(i){
  tmp <- projs[projs$domainNAME == unique(projs$domainNAME)[i],]
  lapply(1:length(unique(tmp$themeNAME)), function(j){
    tmp2 <- tmp[tmp$themeNAME == unique(tmp$themeNAME)[j],]
    F.hierarcplot(col2L = 0.12, col3L = 0.23, col4L = 0.37, col5L = 0.55, col5R = 1, 
              wrapsize1=9, wrapsize2=12, wrapsize3=15, wrapsize=27, wrapsize5=84, 
              fontsize1=1, fontsize2=1, fontsize3=1, fontsize4=0.75, fontsize5=0.7, 
              dat=tmp2)
  })
})

```


## One domain at a time

### `r unique(projs$domainNAME)[1]`
``` {r, eval=T, fig.height=11, fig.width=8.5, dpi=100, dev='tiff', fig.path="figures/", eval=F}
tmp <- projs[projs$domainNAME %in% unique(projs$domainNAME)[2],]
tmp2 <- tmp[tmp$themeNAME == unique(tmp$themeNAME)[1],]

F.hierarcplot(col2L = 0.12, col3L = 0.23, col4L = 0.37, col5L = 0.55, col5R = 1, 
              wrapsize1=9, wrapsize2=12, wrapsize3=15, wrapsize=27, wrapsize5=84, 
              fontsize1=1, fontsize2=1, fontsize3=1, fontsize4=0.75, fontsize5=0.7, 
              domcol="#558aca", thmcol="#558aca", cluscol="#558aca",
              dat=tmp2)


  lapply(1:length(unique(tmp$themeNAME)), function(j){
    tmp2 <- tmp[tmp$themeNAME == unique(tmp$themeNAME)[j],]
  })
```


### `r unique(projs$domainNAME)[2]`

### `r unique(projs$domainNAME)[3]`

### `r unique(projs$domainNAME)[4]`


# Tabular format


``` {r setup, echo=F, message=F, warning=F, eval=F}
source("1.SetupScript.R")
```

``` {r, eval=F}
projs <- read.csv("dataTables/qry_bamPROJECTSflat.csv", header=T)
kable(head(projs), row.names=F)
```

# Plot in tabular format. 

``` {r, clean.table, echo=F, eval=F}
allproj <- data.frame(Domain=projs$Domain, Theme=projs$Theme, Cluster=projs$Cluster, Project=paste(projs$Project, " [", projs$Lead, "]", sep=""), Status=projs$Project.Status)

allproj <- allproj[!is.na(allproj$Domain),]
allproj <- allproj[allproj$Domain != "",]
allproj <- allproj[!duplicated(allproj),]
allproj <- allproj[!allproj$Status %in% c("ABANDONED", "MERGED", "MORPHED"),]

allproj$Domain <- factor(allproj$Domain, levels=domains$Domain[domains$Domain.Number])
allproj$Theme <- factor(allproj$Theme, levels=themes$Theme[order(themes$Theme.Order)])
allproj$Cluster <- factor(allproj$Cluster, levels=clusters$Cluster[order(clusters$Order)])

allproj <- allproj[order(allproj$Domain, allproj$Theme, allproj$Cluster, allproj$Project),]

allproj$Domain <- as.character(allproj$Domain)
allproj$Theme <- as.character(allproj$Theme)
allproj$Cluster <- as.character(allproj$Cluster)
allproj$Project <- as.character(allproj$Project)
``` 

### All currently active, queued, or proposed projects, including those not led by BAM team members

``` {r, echo=F, eval=F}
subproj <- allproj[allproj$Status %in% c("ACTIVE", "IDEA", "ONGOING", "QUEUED", "STALLED", "NOT BAM"),]

subproj$Domain[duplicated(subproj$Domain)] <- " \" "
subproj$Theme[duplicated(subproj$Theme)] <- " \" "
subproj$Cluster[duplicated(subproj$Cluster)] <- " \" "

kable(subproj[c("Domain", "Theme", "Cluster", "Project")], row.names=F)
```

### Historical record of complete and active projects 
Only includes those summarized on SharePoint

``` {r, echo=F, eval=F}
allproj$Domain[duplicated(allproj$Domain)] <- " \" "
allproj$Theme[duplicated(allproj$Theme)] <- " \" "
allproj$Cluster[duplicated(allproj$Cluster)] <- " \" "

kable(allproj[c("Domain", "Theme", "Cluster", "Project", "Status")], row.names=F)
```

