---
title: "2018 BAM Workplan"
author: "Projects worked on in 2017-18"
output:
  word_document:
    reference_docx: styles/ProjectHierarchy.docx
---

**Current as of: `r format(Sys.Date(), "%B %e, %Y")`**

``` {r setup, echo=F, message=F, warning=F}
source("1.SetupScript.R")
```

### Load all projects currently documented in our Workplan Database

``` {r}
projs <- read.csv("dataTables/qry_bamPROJECTSflat.csv", header=T)
```

### Load all project updates and then subset for those on which I received an update between April 1, 2017 and March 31, 2018

``` {r}
updates  <- read.csv("dataTables/projectUPDATES.csv", header=T)

#Fix date formate
tmp1 <- as.character(updates$reportDATE)
tmp2 <- unlist(lapply(strsplit(tmp1, " ", fixed=T), function(x) {x[1]}))
tmp3 <- strptime(tmp2, "%m/%d/%Y")
tmp4 <- as.Date(tmp3)

updates$reportDATE <- tmp4 # bring fixed date back into data.frame

daterange.2017_2018 <- seq(as.Date("2017-04-01"), as.Date("2018-03-31"), by="1 day")

updates.1718 <- updates[updates$reportDATE %in% daterange.2017_2018,]

colnames(updates.1718)[which(colnames(updates.1718) == "PROJECT")] <- "PROJECT.ID"

projects.1718 <- unique(updates.1718$PROJECT.ID)
rm(tmp1, tmp2, tmp3, tmp4,daterange.2017_2018)
```

### Subset all projects table for those that were active in the 2017-18 fiscal year

Indicated by those for which Nicole documented a report in the BAM Workplan Database between April 1, 2017 and March 31, 2018

``` {r}
projs.1718 <- subset(projs, projs$ProjID %in% projects.1718) #subset for active this reporting year
projs.1718 <- projs.1718[order(projs.1718$domainNAME, projs.1718$themeNAME, projs.1718$clusterNAME, projs.1718$Proximity, projs.1718$PROJECTname),] # reorder 
```

``` {r}
projs.s <- split(projs.1718, projs.1718$domainNAME) # split by domain
```


``` {r}
kable(projs.s[[1]][c("domainNAME", "themeNAME","clusterNAME", "PROJECTname", "PROJECTpurpose")])

kable(projs.s[[2]][c("domainNAME", "themeNAME","clusterNAME", "PROJECTname", "PROJECTpurpose")])

kable(projs.s[[3]][c("domainNAME", "themeNAME","clusterNAME", "PROJECTname", "PROJECTpurpose")])

kable(projs.s[[4]][c("domainNAME", "themeNAME","clusterNAME", "PROJECTname", "PROJECTpurpose")])


```



